\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue]{hyperref}

\usepackage[draft]{changes}
\usepackage[noend]{algorithm2e}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage[misc,geometry]{ifsym}

\usepackage{csvsimple}
\usepackage{verbatim}

\usepackage[skip=5pt]{caption}
\usepackage[skip=0pt]{subcaption}
\captionsetup[figure]{font=small}
\captionsetup[table]{font=small}

\DeclareMathOperator{\compass}{compass}
\DeclareMathOperator{\circletool}{circle}
\DeclareMathOperator{\linetool}{line}
\DeclareMathOperator{\anglebi}{Angle Bisector}
\usepackage{array}

\usepackage[compact]{titlesec}
    

\usepackage{placeins}
\let\Oldsection\section
\renewcommand{\section}{\FloatBarrier\Oldsection}
\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}


\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}



\definecolor{greencolor}{rgb}{0,0.5,0}

\newcommand{\maskrcnn}{Mask {R-CNN}\xspace}
\newcommand{\alphapack}{Alpha\xspace}
\newcommand{\betapack}{Beta\xspace}
\newcommand{\gammapack}{Gamma\xspace}
\newcommand{\deltapack}{Delta\xspace}
\newcommand{\epsilonpack}{Epsilon\xspace}
\newcommand{\zetapack}{Zeta\xspace}

\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}
                       {-12\p@ \@plus -4\p@ \@minus -4\p@}
                       {8\p@ \@plus 4\p@ \@minus 4\p@}
                       {\normalfont\large\bfseries\boldmath
                        \rightskip=\z@ \@plus 8em\pretolerance=10000 }}

\makeatother

\begin{document}

\title{Learning to solve geometric construction problems from 
images\thanks{This work was partly supported by the European Regional Development Fund under the projects IMPACT and AI\&Reasoning (reg. no. CZ.02.1.01/0.0/0.0/15\_003/0000468 and CZ.02.1.01/0.0/0.0/15\_003/0000466)
and the ERC Consolidator grant \emph{SMART} no.~714034.
}
}

\author{Jaroslav Macke\inst{1,2}\orcidID{0000-0001-6938-4776} \and
Jiri Sedlar\inst{2}\textsuperscript{(\Letter)}\orcidID{0000-0002-4704-3388} \and
Miroslav Olsak\inst{3}\orcidID{0000-0002-9361-1921} \and
Josef Urban\inst{2}\orcidID{0000-0002-1384-1613} \and
Josef Sivic\inst{2}\orcidID{0000-0002-2554-5301}
}

\authorrunning{J. Macke et al.}
\institute{Charles University in Prague, Czech Republic \and
Czech Technical University in Prague, Czech Republic\\
\email{jiri.sedlar@cvut.cz} \and
University of Innsbruck, Austria}
\maketitle
\begin{abstract}
We describe a purely image-based method for finding geometric constructions with a ruler and compass in the Euclidea geometric game. The method is based on adapting the \maskrcnn state-of-the-art visual recognition neural architecture and adding a tree-based search procedure to it. In a supervised setting, the method learns to solve all 68 kinds of geometric construction problems from the first six level packs of Euclidea with an average 92\% accuracy. When evaluated on new kinds of problems, the method can solve 31 of the 68 kinds of Euclidea problems. We believe that this is the first time that purely image-based learning has been trained to solve geometric construction problems of this difficulty.



\keywords{computer vision \and visual recognition \and automatic geometric reasoning \and solving geometric construction problems}
\end{abstract}

\input{section_1_Introduction}
\input{section_2_RelatedWork}
\input{section_3_Euclidea}
\input{section_4_mrcnn}
\input{section_5_unseen_levels}
\input{section_6_experiments}
\input{section_7_conclusion}

\phantomsection
\let\Origclearpage\clearpage
\let\clearpage\relax

\bibliographystyle{unsrt}
\bibliography{bibliography}
\let\clearpage\Origclearpage

\end{document}
