%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
\let\openright=\clearpage

%% Settings for two-sided (duplex) printing
% \documentclass[12pt,a4paper,twoside,openright]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{14.2mm}
% \setlength\evensidemargin{0mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage{xcolor}         % typesetting in color
\usepackage{subfig}
\usepackage{csvsimple}
\usepackage{longtable}



%ruled,vlined
\usepackage[]{algorithm2e}
\usepackage{multirow}
%should prevent images floating to another sections
\usepackage{placeins}

\let\Oldsection\section
\renewcommand{\section}{\FloatBarrier\Oldsection}

\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}

\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}
%\usepackage[section]{placeins}
%\usepackage[subsection]{placeins}
%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
%TODO: official name
\def\ThesisTitle{Learning to solve geometric construction problems from images}

% Author of the thesis
\def\ThesisAuthor{Bc.~Jaroslav Macke}

% Year when the thesis is submitted
\def\YearSubmitted{2021}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Software and Computer Science Education}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

% Thesis supervisor: name, surname and titles
\def\Supervisor{Dr.~Ing.~Josef Šivic}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Czech Institute of Informatics, Robotics and Cybernetics (CIIRC CTU)}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Artificial Intelligence}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I would like to thank my supervisors Dr.~Ing.~Josef Šivic and  Mgr.~Jiří\newline Sedlář~Ph.D. This thesis would not be possible without theirs guidance, patience and their enthusiasm.
\newline
Also I would like to thank Mgr.~Miroslav Olšák~Ph.D. for sharing and explanation of his Euclida code.\newline
Most importantly I would like to thank my parents, the closest and family for their support.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{
Geometric constructions using ruler and compass are being solved for thousands of years. Humans are capable of solving these problems without explicit knowledge of the analytical models of geometric primitives present in the scene. On the other hand, most methods for solving these problems on a computer require an analytical model. In this thesis, we introduce a method for solving geometrical constructions with access only to the image of the given geometric construction. The method utilizes Mask {R-CNN}, a convolutional neural network for detection and segmentation of objects in images and videos. Outputs of the Mask {R-CNN} are masks and bounding boxes with class labels of detected objects in the input image. In this work, we employ and adapt the Mask R-CNN architecture to solve geometric construction problems from image input. We create a process for obtaining geometric construction steps from masks obtained from Mask R-CNN, and we describe how to train the Mask R-CNN model to solve geometric construction problems. However, solving geometric problems this way is challenging, as we have to deal with object detection and construction ambiguity. There is possibly an infinite number of ways to solve a geometric construction problem. Furthermore, the method should be able to solve problems not seen during the training. 
To solve unseen construction problems, we develop a tree search procedure that searches the space of hypothesis provided by the Mask {R-CNN} model. We describe multiple components of this model and experimentally demonstrate their benefits. As experiments show, our method can learn constructions of multiple problems with high accuracy. When the geometric problem is seen at training time, the proposed approach learns to solve all 68 geometric construction problems from the first six level packs of the geometric game Euclidea with an average accuracy of 92\%. The proposed approach can also solve new geometric problems unseen at training. In this significantly harder set-up, it successfully solves 31 out of these 68 geometric problems.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{computer vision}, {visual recognition}, {automatic geometric reasoning}, {solving geometric construction problems}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{macros}

% Title page and various mandatory informational pages
\DeclareMathOperator{\compass}{compass}
\DeclareMathOperator{\circletool}{circle}
\DeclareMathOperator{\linetool}{line}
\newcommand{\DOF}{DOF}
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the master thesis

\tableofcontents

%%% Each chapter is kept in a separate file
\include{en/chap01_preface}
\include{en/chap02_Euclidea}
\include{en/chap03_TreeSearch}
\include{en/chap04_SuperisedSection}
\include{en/chap05_UnseenLevels}
\include{en/chap06_Experiments}
\include{epilog}




%%% Bibliography
\bibliographystyle{unsrt}
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
%\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
%\listoftables
\appendix
\include{en/Apendix}
%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
%\chapwithtoc{List of Abbreviations}

%%% Attachments to the master thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 72/2017.

%\chapter{Attachments}

%\section{First Attachment}

\openright
\end{document}
